Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = cols[[catal]], fill = cols[[catal]]) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
       #ggtitl(paste("Median title length (", catal, ")", sep = "")) +
       ggtitle("Figure 4") +
       xlab("Decade") +
       ylab("Title length (words)")
}

#library(gridExtra)
#grid.arrange(pics[[1]], pics[[2]], nrow = 1)

@@

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Decade") +
     scale_fill_stata() 
     if (varname == "n") {
       p <- p + #ggtitl(paste("Title count (", catalogue, ")", sep = "")) + 
                ylab("Title count (%)") 
     }
     if (varname == "paper") {
       p <- p + #ggtitl(paste("Paper (", catalogue, ")", sep = "")) +
                ylab("Paper (%)")        
     }
     if (varname == "publishers") {
       p <- p + #ggtitl(paste("Publishers (", catalogue, ")", sep = "")) +
                       ylab("Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = "")) 
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))

@@

}
}
library(gridExtra)
pics[[1]] <- pics[[1]] + ggtitle("Figure 5") 
grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

@@

# TITLE COUNT
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
      xlab("Decade") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)")) +
      #ggtitle("Figure 11")      
      #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
      ggtitle(paste("Figure 11:", place, " (", catalogue, ")", sep = ""))

@@

   p <- ggplot(dfss,
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Decade") +
      ylab("Title count (%)") 
      #ggtitle(paste(myplace, "/", catalogue)) +
      if (cnt == 0) {
        p <- p + labs(title = "Figure 16")
	cnt <- 1
      }

@@

grid.arrange(pics[[1]],
             pics[[8]], pics[[9]], pics[[10]], 
             nrow = 2)
rm(pics)
```

>>>>

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
cols <- list(Fennica = "blue", Kungliga = "darkred")
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = cols[[catal]], fill = cols[[catal]]) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
       #ggtitl(paste("Median title length (", catal, ")", sep = "")) +
       xlab("Decade") +
       ylab("Title length (words)")
}

pics[[unique(df$catalog)[[1]]]] <- pics[[unique(df$catalog)[[1]]]] + labs(title = "Figure 4")

@@

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Decade") +
     scale_fill_stata() 
     if (varname == "n") {
       p <- p + labs(subtitle = paste("Title count (", catalogue, ")", sep = ""), y = "Title count (%)")
     }
     if (varname == "paper") {
       p <- p + labs(subtitle = paste("Paper (", catalogue, ")", sep = ""), y = "Paper (%)")
     }
     if (varname == "publishers") {
       p <- p + labs(subtitle = paste("Publishers (", catalogue, ")", sep = ""), y = "Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = "")) 
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))

@@

}
}
library(gridExtra)
#pics[[1]] <- pics[[1]] + ggtitle("Figure 5") 
grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], top = "Figure 5", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
rm(pics)
```

@@

# TITLE COUNT
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
      xlab("Decade") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)")) +
      #ggtitle("Figure 11")      
      #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
      ggtitle(paste("Figure 11: ", place, " (", catalogue, ")", sep = ""))

@@

   p <- ggplot(dfss,
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Decade") +
      ylab("Title count (%)")

@@

grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 16", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))

rm(pics)
```
